Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-04-04 Paper/paper.tex
update
fixed equilibium/a

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight
    \and
        Izabela Komenda*
    \and
        Jeff Griffiths}

@@

The following result is a sufficient condition for the existence of equilibrium:\\

@@

We let $\widetilde T$ denote the sum of throughputs at Nash Equilibria obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

@@

\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

@@

Clearly, as the demand change increases, the Nash equilibrium thresholds decrease.
This is due to the fact that both CCUs are attempting to divert their patients in less busy states as these states become rarer.
If one CCU diverts early, the other will follow suit (both CCUs incrementally reacting to each other.
As a result the Nash equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
As the demand increases even further the Nash equilibria remain at $(0,0)$ and the PoA decreases.

Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.

@@

A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:

>>>>

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight*
    \and
        Izabela Komenda
    \and
        Jeff Griffiths}

@@

The following result is a sufficient condition for the existence of a equilibrium:\\

@@

We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

@@

Also, for very low values of demand, cooperation can be obtained with no target.
\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

@@

Clearly, as the demand change increases, the Nash equilibrium thresholds decrease.
This is due to the fact that both CCUs are attempting to divert their patients in less busy states as these states become rarer.
If one CCU diverts early, the other will follow suit (both CCUs incrementally reacting to each other.
As a result the Nash equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
As the demand increases even further the Nash equilibrium remains at $(0,0)$ and the PoA decreases.

Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.
We see that as demand increases this value also increases.
Also, for very low values of demand, cooperation can be obtained with no target.
For the actual demand ($x=0$) a target value of $t=0.72$ is once again recommended.

@@

A result is proved that allows for the assertion of existence of a Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
